\documentclass{skvitae}
\usepackage{polyglossia}
\setmainlanguage{english}
\usepackage{csquotes}
\usepackage{ragged2e}

\SetupContactInfo{
	name		= {Simon Sigurdhsson},
	title		= {---},
	company = {---},
	street  = {Engdahlsgatan 6C},
	zip 		= {SE--41259},
	country = {Sweden},
	city 		= {Göteborg},
	email 	= {Sigurdhsson@gmail.com},
	web 		= {http://sigurdhsson.org},
	%phone   = {},
	mobile  = {+46703293054},
	github  = {urdh},
}

\begin{document}
	\RaggedRight
	\maketitle

	%\section{Summary}
	%\ind 50-60 words

	\section{Education}
	\begin{itemize}
		\item Master of Science in Engineering Mathematics and Computational Science, Chalmers University of Technology, 2008--current.%
		\item {Master's thesis: \enquote{Solving max-sum problems with the in-the-middle heuristic}}.%
		\item {Bachelor thesis: \foreignquote{swedish}{Statistisk bildanalys av handgester för människa-dator-interaktion}}.
	\end{itemize}

	\section{Work experience}
	\begin{itemize}
		\item[2013] Summer job (developer in Verification efficiency) at Volvo Car Corporation, Göteborg. %
		    \textit{Developed C\#.NET software using CAN and GPIB to automate testing of FM receivers in infotainment systems.}
		\item[2006--2008] Distributor at \emph{SDR Svensk Direktreklam}, Trelleborg.
	\end{itemize}

	\medskip
	\subsection{Extracurricular activities}
	\begin{itemize}
		%\item[2012--2013] Editor for \emph{Fysikteknologsektionens informationsblad}, Göteborg.
		\item[2012--2013] Treasurer for \emph{Chalmers Studentkårs Film- och Fotocommitté}, Göteborg.
		\item[2011--2014] Photographer for \emph{Chalmers Studentkårs Film- och Fotocommitté}, Göteborg.
		\item[2010--2011] Secretary of the board of \emph{Fysikteknologsektionen}, Göteborg.
		\item[2009--2010] Member of \emph{Fysikteknologsektionens sexmästeri}, Göteborg.
		\item[2009--2011] Editor for \emph{Fysikteknologsektionens informationsblad}, Göteborg.
	\end{itemize}

	\section{Skills}
	\subsection{Language}
	\begin{itemize}
		\item Swedish (native language).
		\item English (fluent both in speech and in writing).
	\end{itemize}

	\medskip
	\subsection{IT skills}
	\begin{itemize}
		\item Good skills: CSS, C, C++, C\#.NET, Git, HTML, \LaTeX, Mathematica, MATLAB, Microsoft Office, Python, R, Ruby.
		\item Basic skills: CANalyzer, Comsol, Fortran, Java, Microsoft Visual Studio, PHP, Subversion.
	\end{itemize}

	\medskip
	\subsection{Miscellaneous}
	\begin{itemize}
		\item Holder of a driver's license (B) since 2008.
		\item References available upon request.
	\end{itemize}
\end{document}
